---
title: "Cubs_DataAnalysis_Viz"
author: "Lauren Wehausen"
date: "9/1/2022"
output: github_document
---

First, let's load the data:
```{r}
cubs <- read.csv("https://raw.githubusercontent.com/gjm112/DSCI401/main/data/cubs_all_time.csv")
```

Now, let's take a look at the data we're working with:
```{r}
head(cubs, 3)
```

How many total games have the Cubs won and lost between 1876 and 2022?
```{r}
sum(cubs$W)
sum(cubs$L)
```
Total games won: 11141
Total games lost: 10592

What year did the Cubs score the most runs? What year did the Cubs score the fewest runs? Do you have any thoughts about the year that the Cubs scored the fewest runs?
```{r}
#Find the maximum number of runs.
max(cubs$R)
#Find what year the value found previously, occurred. 
cubs$Year[which.max(cubs$R)]
#Find the minimum number of runs.
min(cubs$R)
#Determine what year the previously found value occurred. 
cubs$Year[which.min(cubs$R)]
```
The Cubs had the most runs, 1056, in 1894 and the least runs, 265, in 2020. 
The year 2020 was probably the worst because it was when COVID first began.

In how many seasons was the Cubs total attendance (i.e. the variable
Attendance) over 3 million?
```{r}
attend2 <- cubs$Attendance[!is.na(cubs$Attendance)] 
sum(attend2 > 3000000)
```

There were 12 seasons where the attendance was greater than or equal to 3 million. 














